The Bug Catalog of the Maven Ecosystem

### 2014-02-17 docs/msr.tex
added content

A typical processing cycle of a worker included the following steps: after
the worker spawned, it requested a task from the queue. This task contained
the {\sc jar} name, which was typically a project version that was downloaded locally.
First, specific {\sc jar} metadata were calculated and stored. Such metadata included
its size, its dependencies, and a number that represented the chronological order of the
release. This order was derived from an {\sc xml} file that
accompanies every project in the Maven repository called {\it
maven-metadata.xml}. Then, FindBugs was invoked by the worker and its results were
also stored in the data repository. 
FindBugs separates software bugs into nine
categories\footnote{\url{http://findbugs.sourceforge.net/bugDescriptions.html}}
(including Bad Practice, Security, Performance and others)
and reports bug collections that include all the bugs discovered in a
{\sc jar} file. For every registered bug, there are numerous accompanying features
like the class, the method and the line that the bug was found.
When the task was completed the queue
was notified and the next task was requested. A schematic representation of
the data processing architecture can be seen in Figure~\ref{fig:arch}.

\begin{figure} [h]
  \begin{center}
    \includegraphics[scale=0.73]{figures/arch.pdf}
  \end{center}
  \caption{The data processing architecture.}
  \label{fig:arch}
\end{figure}

@@

As we mentioned earlier our data was stored in a
Mongo{\sc db} database, thus all the data were 
converted to the {\sc json} format. FindBugs output data is in {\sc xml} format. The conversion was a straight forward mapping
of the {\sc xml} elements to {\sc json} objects. In addition, to the FindBugs data, we added a metadata section, which contained
several additional information regarding the jar file that has been processed (Table~\ref{tbl:metadata-description}). The following listing contains an excerpt:

\begin{verbatim}
{"JarMetadata": {"jar_filename": "",
                 "jar_size": "",
                 "version": "",
                 "version_list": "",
                 "artifact_id": "",
                 "group_id": "",
                 "dependencies": ""}, 
 "BugCollection": { /* FindBugs data */ }}
\end{verbatim}

Since Mongo{\sc db} provides a rich query interface, it was easy to either create
queries to find out basic information like:
``how many bad practice bugs exist in the repository", or
create scripts that can help us capture correlations
that could provide valuable findings. Figure~\ref{fig:bug-per} shows how software 
bugs are distributed among the repository.

\begin{table}
\centering
\caption{Jar metadata description}
\label{tbl:metadata-description}
\begin{tabular}{l p{5.0cm}}
 \hline
\verb|jar_filename| & JAR's filename\\
\verb|jar_size| & The size of the JAR file\\
\verb|version| & The version of the project in Maven repository\\
\verb|version_list| & A list of project's version numbers\\
\verb|artifact_id| & The artifact id of the project in Maven repository\\
\verb|group_id| & The group id of the project in Maven repository\\
\verb|dependencies| & List of all dependencies for the project\\
 \hline
 \end{tabular}
\end{table}

@@

@@

The Maven ecosystem has been previously analyzed by
Raemaekers et al.~\cite{RDV13}
to produce the {\it Maven dependency dataset}.
Apart from basic information like individual methods, classes,
packages and lines of code for every {\sc jar}, this dataset
also includes a database with all the
connections between the aforementioned elements.

>>>>

A typical processing cycle of a worker included the following steps: after
the worker spawned, it requested a task from the queue. This task contained
the {\sc jar} name, which was typically a project version that was downloaded locally.
First, specific {\sc jar} metadata were calculated and stored. Such metadata included
its size, its dependencies, and a number that represented the chronological order of the
release. This order was derived from an {\sc xml} file that
accompanies every project in the Maven repository called {\it
maven-metadata.xml}. Then, FindBugs was invoked by the worker and its results were
also stored in the data repository. 
FindBugs separates software bugs into nine
categories\footnote{\url{http://findbugs.sourceforge.net/bugDescriptions.html}}
(including Bad Practice, Security, Performance and others)
and reports bug collections that include all the bugs discovered in a
{\sc jar} file. For every registered bug, there are numerous accompanying features
like the class, the method and the line that the bug was found.
When the task was completed the queue
was notified and the next task was requested.

A threat to the internal validity of our experiment
could be the false alarms of the
FindBugs tool~\cite{AP10, HP04}.
For instance, reported security bugs may not
be applicable to an application's typical use context.
For instance, FindBugs could report an {\sc sql}
injection vulnerability~\cite{RL12}
in an application that receives no external input.
In this particular context, this would be a false positive alarm.

@@

\begin{table}
\centering
\begin{tabular}{l p{5.0cm}}
 \hline
\verb|jar_filename| & {\sc jar}'s filename. \\
\verb|jar_size| & The size of the {\sc jar} file. \\
\verb|version| & The version of the project in the repository. \\
\verb|version_list| & A list of all available version's of this project. \\
\verb|artifact_id| & The artifact {\sc id} of the project in Maven repository. \\
\verb|group_id| & The group {\sc id} of the project in Maven repository. \\
\verb|dependencies| & List of all dependencies for the project. \\
 \hline
 \end{tabular}
\caption{Jar metadata description.}
\label{tbl:metadata-description}
\end{table}

As we mentioned earlier our data was stored in a
Mongo{\sc db} database, thus all the data were 
converted to the {\sc json} format. FindBugs output
data is in {\sc xml} format. The conversion was a
straight forward mapping
of the {\sc xml} elements to {\sc json} objects.
In addition, to the FindBugs data, we added a metadata
section, which contained
several additional information regarding the {\sc jar}
file that has been processed
(see Table~\ref{tbl:metadata-description}).

@@

Since Mongo{\sc db} provides a rich query interface,
it was easy to either create
queries to find out basic information like:
``how many bad practice bugs exist in the repository", or
create scripts that can help us capture correlations
that could provide interesting findings. For instance,
Figure~\ref{fig:bug-per} shows how software 
bugs are distributed among the repository.

Together with our dataset, we have created a series of
scripts to exhibit how it can be used regarding
the evolution of software bugs.
Table~\ref{tbl:bugsperversion} shows the relation between
bugs and time. This relation, can be traced from the number of
bugs per category in each project version. We can then calculate the
Spearman correlations between the defects count and the ordinal
version number across all projects to see if bigger versions relate to
higher or lower defect counts.
The zero tendency though, applies to all versions of all projects together.
Thus, we also performed Spearman correlations between bug counts and version
ordinals in all projects we examined individually. These paint a different picture
from the above table, shown in Figure~\ref{fig:bugsversionscorr}. The
spike in point zero is explained by the large number of projects for
which no correlation could be established---the scale is
logarithmic.
Figure~\ref{fig:bugdiffs}, presents a histogram of the changes
of different bug counts in
project versions. In most cases, a bug count does not change between
versions; but when it does change, it may change upwards or downwards.

\begin{table}[tphp]
    \centering
    \caption{Correlations between version and defects count.}
    \label{tbl:bugsperversion}
    \input{bugsperversion.tex}
\end{table}

\begin{figure*}[p]
  \centering
  \includegraphics[scale=0.30]{bugsversionscorr}
  \caption{Histograms of correlations between bug counts and version
    ordinals per project. In brackets the total population size and
    the number of no correlation instances.}
  \label{fig:bugsversionscorr}
  \centering
  \includegraphics[scale=0.35]{bugdiffs}
  \caption{Changes in bug counts between versions.}
  \label{fig:bugdiffs}
\end{figure*}

To examine the relation between the persistence of different kinds of
bugs we used as a persistence
indicator the number of versions a bug remains open in a project. To
``tag" a bug we created a bug identifier by using the type of the bug,
the method name and the class name in which the bug was found in. We
chose not to use the line number of the location of the bug since it
could change from version to version and after a possible code
refactoring. We grouped the persistence numbers by bug categories and
then performed a Mann-Whitney $U$~\cite{HM98} test among all bug
category pairs. The results are presented in
Table~\ref{tbl:bug_persistence} (at the end of this paper). Cells in
brackets show pairs where no statistically significant difference was
found.

In addition, we explored the relation between defects with the size of a project
version, measured by the size of its {\sc jar} file by carrying out
correlation tests between the size and the defect counts for each
project and version. The results can be seen in
Table~\ref{tbl:jarsizecorr}.

Finally, Figure~\ref{fig:corrplot} presents the pairwise correlations
between all bug categories. To establish these correlations,
we calculated the
correlations between the number of distinct bugs that appeared in
a project throughout its lifetime.

\begin{table}[hbt]
    \centering
    \caption{Correlations between {\sc jar} size and defects count.}
    \label{tbl:jarsizecorr}
    \input{jarsizecorr.tex}
\end{table}

@@

The Maven ecosystem has been previously analyzed by
Raemaekers et al.~\cite{RDV13}
to produce the {\it Maven dependency dataset}.
Apart from basic information like individual methods, classes,
packages and lines of code for every {\sc jar}, this dataset
also includes a database with all the
connections between the aforementioned elements.
%Our work goes a step further and includes for every {\sc jar}
%of the repository, all the software bug that it contains.
